---
title: "Week 3 Assignment"
author: "Kim Paulo D. Magboo"
date: "February 11, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## General Instruction

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly.

## Scatterplot of Miles per Gallon and Weight based on the Number of Forward Gears

Using the mtcars data, we perform exploratory data analyis by investigating the relationship of fuel cosumption and weight based on the number of forward gears.  

```{r plotly, message=FALSE}
library(plotly)
mtcars$gear <- factor(mtcars$gear,labels=c('3','4','5'))
plot_ly(mtcars, x =mtcars$wt, y=mtcars$mpg, color=mtcars$gear)
```

## Scatterplot of Miles per Gallon and Weight based on Number of Cylinders

Using the mtcars data, we perform exploratory data analyis by investigating the relationship of fuel cosumption and weight based on the number of cylinders.  

```{r plotly2, message=FALSE}
mtcars$cyl <- factor(mtcars$cyl,labels=c('4','6', '8'))
plot_ly(mtcars, x =mtcars$wt, y=mtcars$mpg, color=as.factor(mtcars$cyl))
```

## End of Presentation